---
title: "p8105_hw5_yw3774"
author: "Yida Wang"
date: "11/12/2021"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(rvest)
library(knitr)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## problem 1
```{r}

url_1 = "https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv"
homic = read_csv(url_1)

```
### summary
This dataset contains `r nrow(homic)` homicides conditions in 50 large U.S. cities with `r ncol(homic)` variables. Missing values exist in victim_race, victim_age, victim_race, and geographical coordindates. Missing values were changed to N/A. 
* Let's create a variable contains city and state
* Then summarize the total number of homicides and unsolved homicides
```{r}
city_state_homic = homic %>% 
  unite(city_state, c("city", "state"), sep = ", ") %>% 
  group_by(city_state) %>% 
  summarise(total_homic = n(),
            total_unsolved = sum(disposition %in% c("Closed without arrest", "Open/No arrest")))
knitr::kable(city_state_homic)
```

For the city of Baltimore, MD, do the two-side test to get estimated proportion and 95% confidence interval.

```{r }
balt_md = city_state_homic %>% 
  filter(city_state == "Baltimore, MD") 
result_prop = 
  prop.test(x = pull(balt_md, total_unsolved),
            n = pull(balt_md, total_homic)) %>% 
  broom::tidy() %>% 
  select(estimate, conf.low, conf.high)
```

Now for all the cities:

```{r warning=FALSE}
homicide_all =
  city_state_homic %>% 
  mutate(prop_test = map2(.x = total_unsolved, .y = total_homic, ~prop.test(x = .x, n = .y)),
         tidy_test = map(.x = prop_test, ~broom::tidy(.x))) %>% 
  select(-prop_test) %>% 
  unnest(tidy_test) %>%
  select(city_state, estimate, conf.low, conf.high)
```

Create a plot to show the results:

```{r}
homicide_all %>% 
  mutate(
    city_state = fct_reorder(city_state, estimate)
  ) %>%
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  coord_flip() +
  labs(x = "City",
       y = "Proportion",
       title = "95% Confidence interval and Estimated Proportion \n of Unsolved Homicides Cases in Each City") +
   theme(axis.text.x = element_text(vjust = 0.5, hjust = 0.5))
```

# problem 2
```{r}
data_path = str_c("data/", list.files(path = "data/."))

new_data = tibble(
  files_names = list.files(path = "data/."),
  participants = purrr::map(data_path, read_csv) 
) %>% 
  separate(files_names, into = c("arm","ID"), sep = "_") %>% 
  separate(col = "ID", into = c("id", "csv")) %>%
  mutate(
    arm = recode(arm, con = "control", exp = "experiment" )
    ) %>% 
  select(-csv) %>% 
  unnest(participants) %>%
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    names_prefix = "week_",
    values_to = "observations"
  ) %>% 
  mutate(week = as.numeric(week)) %>%
  mutate(arm = as.factor(arm))
  
new_data
  
```
Make a plot for observations 
```{r}
new_data %>% 
 ggplot(aes(x = week, y = observations, color = id)) +
  facet_grid(. ~ arm) +
  geom_line() +
   labs(
    title = "comparison between groups",
    x = "week",
    y = "value"
    )
```

From the plot, we can see that from week 1 to week 8, there was a significant trend of general increase of the observed value in the experimental group, which is from around 0-3.75 to 3.75-7. However, there is no significant trend of increase or decrease for the observed value in the control group as weeks passed. Observed values maintained around 0 to 2.5 from week 1 to week 8.


# problem 3


```{r}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```
* For numeric variables, you should fill in missing values with the mean of non-missing values
* For character variables, you should fill in missing values with "virginica"
```{r}
replace = function(x) {
  
  if (is.numeric(x)) {
   x = replace_na(x, mean(x, na.rm = TRUE))
    }
  else if (is.character(x)) {
    x = replace_na(x, "virginica")
  }
}

iris_missing_replace = map(iris_with_missing, replace)

new_iris = iris_missing_replace %>% 
  as_tibble()
```

Check the result
```{r}
new_iris %>%
  summarise_all(~ sum(is.na(.)))
```

